---
title: "Reproducible Research Course Project"
author: "YE"
date: "3 juillet 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

It is now possible to collect a large amount of data about personal movement using activity monitoring devices such as a Fitbit, Nike Fuelband, or Jawbone Up. These type of devices are part of the “quantified self” movement – a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. But these data remain under-utilized both because the raw data are hard to obtain and there is a lack of statistical methods and software for processing and interpreting the data.


## Data

*   Dataset: Activity monitoring data [52K]

The variables included in this dataset are:

*   steps: Number of steps taking in a 5-minute interval (missing values are coded as NA)
*   date: The date on which the measurement was taken in YYYY-MM-DD format
*   interval: Identifier for the 5-minute interval in which measurement was taken

The dataset is stored in a comma-separated-value (CSV) file and there are a total of 17,568 observations in this dataset.

## Assignment

###  Loading and processing data

1.  Load data
```{r, echo=TRUE}
data <- read.csv('activity.csv', na.strings = c("", "NA"))
dim(data)

```
2.  Preprocessing data
```{r}
#Remove NAs
processData = data[!is.na(data$steps), ]  
dim(processData)

# Keep a list of all possible days
uniqueDates <- unique(processData$date)

# Keep a list of all possible intervals
uniqueIntervals <- unique(processData$interval)
```

### What is mean total number of steps taken per day?

1.  Total number of steps taken per day
```{r, echo=TRUE}
    NbrStepsDate <- aggregate(processData$steps, list(processData$date), sum)
    colnames(NbrStepsDate) <- c("date", "steps")
    
    Smean   <- mean(NbrStepsDate$steps)
    Smedian <- median(NbrStepsDate$steps)
    
    # Steps mean
    Smean
    
    # Steps median
    Smedian
    
```

2.  Histogram of the total number of steps taken each day.

```{r, echo=TRUE}

library(ggplot2)

ggplot(data=NbrStepsDate, aes(x=steps)) +
  geom_histogram(fill="#f0ad4e") +  
  ggtitle("Number of steps per Day") +
  labs(x="Steps/Day", y="Number of times in a day")
```

### What is the average daily activity pattern?

1.  Time series plot of the average number of steps taken

```{r}
    # Split the data according to the interval
intSplit <- split(processData$steps, processData$interval)

# Find the average amount of steps per time interval - ignore NA values
AVGStepsPerInt <- sapply(intSplit, mean, na.rm=TRUE)

# Plot the time-series graph
plot(uniqueIntervals, AVGStepsPerInt, type="l",
     main="Average number of steps per interval across all days", 
     xlab="Interval", ylab="Average # of steps across all days", 
     lwd=2, col="blue")

# Find the location of where the maximum is
maxIntervalDays <- max(AVGStepsPerInt, na.rm=TRUE)
maxIndex <- as.numeric(which(AVGStepsPerInt == maxIntervalDays))

# Plot a vertical line where the max is
maxInterval <- uniqueIntervals[maxIndex]
abline(v=maxInterval, col="red", lwd=3)
```

2.  The 5-minute interval that, on average, contains the maximum number of steps

```{r}
maxInterval

```

### Imputing missing values

1.  Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with NAs)

```{r}

isNA <- sum(is.na(data$steps))
isNA
```

2.  Devise a strategy for filling in all of the missing values in the dataset. The strategy does not need to be sophisticated. For example, you could use the mean/median for that day, or the mean for that 5-minute interval, etc.


3.  Create a new dataset that is equal to the original dataset but with the missing data filled in.



